30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-18 paper.tex
Replaced "ditch" with "discontinue" and removed the unnecessary "such as onion routing" example.

	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}. In this section, we will explain the various components of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.

>>>>

	In 2002, it was decided to discontinue the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}. In this section, we will explain the various components of Tor, the structure of the network, circuit creation and disadvantages of Tor.
